---
title: "Important Research Paper"
author: Clinician One, The Statistician, Clinician Two, Senior Author
output: rmarkdown::word_document
---


```{r label = "setup", include = FALSE}
library(ggplot2)
theme_set(theme_bw())
options(qwraps2_markup = "markdown")
knitr::opts_chunk$set(echo = FALSE, results = "hide")

```
```{r label = "load_data", include = FALSE}
orig <- new.env()
data(diamonds, package = "ggplot2", envir = orig)
data(diamonds, package = "ggplot2", envir = .GlobalEnv)
diamonds <- subset(diamonds, carat <= 3)

# check
dim(orig$diamonds)
dim(diamonds)

# discretized carat weights
diamonds$carat2  <- droplevels(cut(diamonds$carat, breaks = seq(0, 3, by = 0.5)))
table(diamonds$carat2, useNA = "always")
```




```{r label = "get_results_for_absract"}
invisible(source("03-Results.R"))
```


# Abstract

**Purpose:** Building up a clinical research article in parts is one way to
organize an your work.  Some writers may find having several small files,
each with a specific focus, easier to work with than one all encompassing
large file.  The files presented in this directory are and example of
building a clinical research manuscript with knitr::spin and child documents.

**Methods:** Example files and a work flow are presented.  A subset of the
diamonds data set from the ggplot2 is used for the examples.

**Results:** _hightlight results here, e.g.  Diamonds ranging between 1.0 and 1.5
carats in weight have a mean price of
`r  cis[["carat2(1,1.5]"]]  `
US dollars._

**Conclusions:** _hightlight conclusions_

`r  knitr::spin_child("01-Introduction.R")  `
`r  knitr::spin_child("02-Methods.R")  `
`r  knitr::spin_child("03-Results.R")  `
`r  knitr::spin_child("04-Discussion.R")  `

# References

<div id="refs"></div>

# Table Captions

**Table 1:** Summary of the diamonds data set.

# Figure Captions

**Figure 1:** The diamonds data set: Scatter plot of price by carat weight.

**Figure 2:** The diamonds data set: Price by carat weight.  Mean price for
each set of diamonds is plotted as a point on the violin plot.

**Figure 3:** Tukey HSD for differeces in mean price of diamonds by carat
weight groups.

`r knitr::spin_child("Tables.R") `
`r knitr::spin_child("Figures.R") `
